---
title: "Pareto SCP"
author: "Stanley Mastrantonis"
date: "2023-05-24"
output: html_document
---

# Libraries
```{r, echo=FALSE}
library(raster)
library(Rcpp)
library(gdistance)
```
# Get and set the current directory path

```{r}
current_dir <- getwd()
setwd(current_dir)
```

#Functions
```{r}
source('ReZone_Functions.R') # Source the Rezone functions, please contact author for the heuristic function
```

#Study Parameters
```{r}
res <- 1  # Study resolution
forage <- 75 # Set vegetation radius parameter
buffer <- 25 # Set exponential decay buffer
breaks <- seq(0, 1, by = 0.01)
rbPal <- colorRampPalette(c('red','blue'))
cols_out <- colorRampPalette(c('white',"pink", "yellow", "lime green"))(length(breaks) - 1)
```


#Data Read-in
```{r}
data_dir <- file.path(getwd(), "data")
setwd(data_dir) # Set directory of data

res_1_mat <- as.matrix(read.csv('p_res_1.csv'), rownames.force = FALSE)
res_2_mat <- as.matrix(read.csv('p_res_2.csv'), rownames.force = FALSE)
ac <- raster('sp_1_ac.tif')
study_area <- as(extent(ac), 'SpatialPolygons')
perm <- 1 - ac
conf <- raster('conflict.tif') # Load in conflicting spatial layer
```

#Grid and Matching
```{r}
grid <- get_topologies(study_area, res)
res_1_match <- grid[whichmindist_func(grid, res_1_mat),]
res_2_match <- grid[whichmindist_func(grid, res_2_mat),]
```


#Kernel Function
```{r}
value_df <- sdf(0, forage)
max_kern <- max_kern_func(res_1_match, res_2_match)
```

# evaluate landscape 
```{r}
res_val = res_value_function(res_1_match, study_grid_matrix,ac)
max_val = landscape_value_sum(res_1_match, res_2_match, res_val)
cell_value = cellvalue(res_1_match, res_2_match, res_val)
```

#Plot Results
```{r}
Col <- rbPal(50)[as.numeric(cut(cell_value$val, breaks = 50))]
ras_value <- raster_value_func(cell_value, grid)
plot(ras_value, interpolate = TRUE)
points(res_1_match, cex = 1.7, pch = 20, col = 'black')
points(res_2_match, cex = 1.7, pch = 20, col = 'blue')
```

#Least Cost Pathing
# will print a number after each path has completed
```{r}
pass <- passage_func(res_1_match, res_2_match, cell_value, ras_value, perm)
plot(pass, col = cols_out, interpolate = TRUE)
```

#Pareto Optimization
#######IMPORTANT#######################################################
#######click on the fontier plot to choose a land use allocation 'finish' in top right of plot
##### run this below line of code:

par_out <- pareto_func(ras_value, conf) # Read above

```{r}
plot(ras_value)
plot(par_out, col = 'red', legend = FALSE, add = TRUE)
```




